Probability Distribution Checks

### 2017-03-23 Probability_distribution_checks.Rmd
Edits for clarity

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ProjectTemplate)
load.project()
```
# 2015
## 2015 Check probability distribution fit for leaf sheath blight

@@

# 2016

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ProjectTemplate)
load.project()
```

## 2015 Check probability distribution fit for leaf sheath blight

@@
